% !TEX program = xelatex

\documentclass{resume}
\pagestyle{empty}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=cyan,
    filecolor=magenta,
    urlcolor=blue,
}

\urlstyle{same}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{MEUKAM Arnaud}

\basicInfo{
  \email{ameukam@gmail.com} \textperiodcentered\
  \phone{(+33) 768-018-418} \textperiodcentered\
  \item France \textperiodcentered\
}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Supinfo International University (SUPINFO)}, France}{2014 -- 2017}
\textit{B.S. with Honours} in Computer Science
\datedsubsection{\textbf{Cosendaï Adventist University}, Cameroon}{2005 -- 2011}
\textit{B.S.} in Computer Maintenance

\section{\faUsers\ Experience}
\datedsubsection{\textbf{RadioFrance (through alter way)} Paris, France}{Nov. 2018 -- Present}
\role{Production Engineer}

\datedsubsection{\textbf{alter way} Paris, France}{July 2018 -- Present}
\role{Production Engineer}

\datedsubsection{\textbf{Vente Privée} Paris, France}{August 2017 -- Mars 2018}
\role{DevOps Engineer}{}
\begin{itemize}
  \item built and maintained infrastructure based on Kubernetes and Rancher on top of VMware infrastructure
  \item improved continuous integration build systems for containerized .NET Applications
\end{itemize}

\datedsubsection{\textbf{INEAT Conseil} Lomme, France}{July 2016 -- Oct. 2016}
\role{Intern}{}
\begin{itemize}
    \item Implemented a global backup strategy for a business application written in PHP using PostgreSQL as DB.
	\item automated creation and setup of development environments using Vagrant and Docker
\end{itemize}

\datedsubsection{\textbf{PLURITECH CVBA} Vilvoorde, Belgium}{July 2015 -- Oct. 2015}
\role{Intern}{}
\begin{itemize}
    \item Apply troubleshooting techniques to provide solutions to the individual needs of CloudAnyWhere clients.
	\item Diagnosed, analyzed and resolved user laptop, PC or handheld devices software and hardware issues.
    \item Installed, upgraded and tested various vendor-based desktop related software, following new releases or upon user requests.
\end{itemize}

\datedsubsection{\textbf{Y-Note} Yaoundé, Cameroon}{Oct. 2013 -- March 2014}
\role{System Administrator}{}
\begin{itemize}
  \item Managed and maintained infrastructure running on OVH
  \item Designed and built backup processes for PostgreSQL DBs with AWS S3 and Glacier
  \item Assisted customers in their use of Y-Note products
\end{itemize}

\datedsubsection{\textbf{ALADJI International} Yaoundé, Cameroon}{May 2012 -- Sept. 2013}
\role{IT Manager}{}
\begin{itemize}
    \item Building, configuration and troubleshooting of server and desktop hardware.
    \item Project management and follow-up of service providers.
	\item Maintenance, maintenance, training, assistance and incident management.
\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Configuration Management: Puppet, Terraform
  \item Containers: Docker, Kubernetes
  \item Databases: PostgreSQL
  \item Programming Languages: Git, Bash, Java
  \item Platforms: Linux, Terraform, GCP
\end{itemize}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Github \url{https://github.com/ameukam}
  \item Kubernetes Contributor
  \item Languages: English - Fluent, French - Native speaker
\end{itemize}

\end{document}
